Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-08-01 Latex/journal_v1/V5/pr.tex
add journal finilized

\begin{abstract}
Taking advantage of both virtual RAN (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems which leads to increase flexibility, Openness, and reduce operational costs and allow them to add new capabilities to the network more quickly.
O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
In this paper, we study the problem of baseband resource allocation and virtual network function (VNF) activation in O-RAN architecture based on their service priority for different types of 5G services includes enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services.
According to the concept of network slicing, the isolation of different types of services in O-DU, O-CU, and user plane function (UPF) is performed.
The limited fronthaul capacity and the restriction of end-to-end delay are considered in this problem.
The optimization of baseband resources includes O-RU assignment, physical resource block (PRB), and power allocation. The main problem is the mixed-integer non-linear programming that is tremendously difficult.
So we broke it down into two different steps that the iterative algorithm solves it.
In the first step, we reformulated and simplified the problem to find the power allocation, PRB assignment, and the number of activated VNFs. In the second step, the O-RU association is carried out.
The proposed method (IAPPVO) is confirmed by the simulation results which illustrate a higher achievable data rate than a baseline scheme that only optimizes one of the baseband resources and the FBDR algorithm described in other papers. Also, the simulation results achieved less end-to-end delay for the proposed method than the FBDR and baseline scheme.

@@

\section{Introduction} 
One of the fifth-generation goals of the wireless system is to achieve the desired QoS (such as rate, delay, power, ...) for different types of services. Network slicing is the best solution for this aim. A network slice is an end-to-end logical network that offers services with special needs.  
Multiple isolated network slices run, manage, and work independently on the same infrastructure. There are several implementations of network slicing, including network core slicing, RAN slicing, and slicing of both sections. 
Different type of services includes enhanced mobile broadband (eMBB), and ultra-reliable low latency communications (URLLC), and massive Machine Type Communications (mMTC) services are introduced in 5th generation of mobile network. Each type of service requires a particular slice of network based on its QoS
\cite{shen2020ai,setayesh2020joint,popovski20185g}.

@@

We solve this problem in two-level iteratively until it converges. In the first level, parameters ($\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}$) are obtained by relaxing and reformulating parameters and turn them into a convex problem; Afterward, we solve it by dual optimization problem.

@@

\subsection{Sub-Problem 1}\label{sub1}
Suppose that $\boldsymbol{G}$ is fixed, we want to obtain $\boldsymbol{P}, \boldsymbol{E}$ and $\boldsymbol{M}$.
Here, we first simplify and relax the parameters to convexify the problem.

@@

0\leq M_s \leq \min\{M^{max}, \alpha_s/\mu_s, \phi_{max}/{3\phi_s}\}

@@

We denote $ \mathfrak{M}_s= \min\{M^{max}, \alpha_s/\mu_s, \phi_{max}/{3\phi_s}\}$.

@@

0\leq \frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s

@@

\frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s

@@

So by reformulating the equation \eqref{constraint16}, we have a new constraint $\forall i, \forall s$ as below,

@@

@@

The complexity of this algorithm is about $O(Slog(S)) + O(R\times \mathfrak{N})$.

@@

@@

The maximum number of VNF for each slice is 20 and the mean arrival rate for eMBB and URLLC is $\lambda  = 300KHz$ and for mMTC $\lambda  = 600KHz$. 

@@

   Minimum data rate for URLLC and mMTC &  5 bits/sec/Hz \\ 

@@

Figure \ref{fig:8}, represents the aggregate throughput concerning the number of UEs and the maximum power for three different mMTC services. mMTC services include a large number of UEs with low data rates and low power.
Assume each service instance requires $1bits/sec/Hz$ data rate and is not sensitive to end-to-end delay. The figure depicts that by increasing the number of UEs in each instance of the service, the aggregate throughput increases. Also, by increasing the maximum power of each UE in each instance of mMTC service, the aggregate throughput rises too.
\begin{figure}
  %\centering 
    \includegraphics[scale = 0.42]{mmTCpower.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput for mMTC services vs. Number of UE in each Service for three different mMTC service instances}
  \label{fig:8}
\end{figure}
\section{Conclusion}\label{conc}
This paper proposed the downlink of the O-RAN system using network slicing for different types of 5G services (eMBB, mMTC, and URLC).
The isolation of various types of services (eMBB, mMTC, and URLC) in O-DU, O-CU, and user plane function (UPF) is accomplished.
Also, the paper aims to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the sum rate. The limited fronthaul capacity and the mean end-to-end delay for each service are considered. 
The problem is mixed-integer non-linear programming that is solved by the two-step iterative algorithm.
In the first step, we reformulated the problem to achieve the number of activated VNFs as a function of data rate. Then we obtain PRB association and power allocation using the Lagrangian method.
Then in the second step, O-RU association is acquired.
The performance of our proposed method (IAPPVO) is compared with the baseline scheme and FBDR in \cite{lee2018dynamic}. 
Also, we assume distinct scenarios for each service (eMBB, URLLC, and mMTC) based on their requirement QoS.
Simulation results depicts that the proposed method (IAPPVO) achieved $18.6\%$ higher data rate than the baseline scheme.
Moreover, simulation results illustrate less delay for the proposed method (IAPPVO) than FBDR and baseline scheme. 
\bibliography{ref}
\end{document}

>>>>

\begin{abstract}
Taking advantage of both virtual RAN (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems. O-RAN leads to increased flexibility, Openness and reduces operational costs, allowing them to add new capabilities to the network more quickly.
O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
In this paper, we study the problem of baseband resource allocation and virtual network function (VNF) activation in O-RAN architecture based on their service priority for different types of 5G services includes enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services.
According to the concept of network slicing, the isolation of different types of services in O-DU, O-CU, and user plane function (UPF) is performed.
The limited fronthaul capacity and the restriction of end-to-end delay are considered in this problem.
The optimization of baseband resources includes O-RU assignment, physical resource block (PRB), and power allocation. The main problem is the mixed-integer non-linear programming that is tremendously difficult.
So we broke it down into two different steps that the iterative algorithm solves it.
In the first step, we reformulated and simplified the problem to find the power allocation, PRB assignment, and the number of activated VNFs. In the second step, the O-RU association is achieved.
The proposed method (IAPPVO) is confirmed by the simulation results which illustrate a higher achievable data rate than a baseline scheme that only optimizes one of the baseband resources and the FBDR algorithm described in other papers. Also, the simulation results attained less end-to-end delay for the proposed method than the FBDR and baseline scheme.

@@

\section{Introduction} 
One of the fifth-generation goals of the wireless system is to achieve the desired QoS (such as rate, delay, power, ...) for different types of services. Network slicing is the best solution for this aim. A network slice is an end-to-end logical network that offers services with specific needs.  
Multiple isolated network slices run, manage, and work independently on the same infrastructure. 
Several implementations of network slicing include network core slicing, RAN slicing, and slicing of both sections. 
Different type of services includes enhanced mobile broadband (eMBB), and ultra-reliable low latency communications (URLLC), and massive Machine Type Communications (mMTC) services are introduced in 5th generation of mobile network. Each type of service requires a particular slice of network based on its QoS.
eMBB requires a higher transmission data rate in comparison with 4G systems. Moreover, eMBB service satisfies the demands of high capacity and considerable coverage.
URLLC requires low latency restrictions and higher reliability of the system.
URLLC contains services such as autonomous vehicles, tactile internet, or remote surgery.
mMTC consists of a vast number of low power Internet of Things (IoT) devices transmitting small payloads to a typical receiver. In addition, mMTC UEs include sensors for sensing, metering, and monitoring devices 
\cite{shen2020ai,setayesh2020joint,popovski20185g,dogra2020survey,kassab2018coexistence,alsenwi2021intelligent}.

@@

We solve this problem in two-level iteratively until it converges. In the first level, parameters ($\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}$) are obtained by relaxing and reformulating parameters to turn them into a jointly-convex problem; Afterward, we solve it by dual optimization problem.

@@

\subsection{Sub-Problem 1}\label{sub1}
Suppose that $\boldsymbol{G}$ is fixed, we want to obtain $\boldsymbol{P}, \boldsymbol{E}$ and $\boldsymbol{M}$.
Here, we first simplify and relax the parameters to convexify the problem.

@@

\alpha_s/\mu_s\leq M_s \leq \min\{M^{max}, \phi_{max}/{3\phi_s}\}

@@

We denote $ \mathfrak{M}_s= \min\{M^{max}, \phi_{max}/{3\phi_s}\}$.

@@

\alpha_s/\mu_s\leq \frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s

@@

\alpha_s/\mu_s\leq \frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s

@@

The left side of this formula leads to $R_{u(s,i)} \geq \lambda_{u(s,i)}$ that is the constraint \eqref{c16-2}. 
For the right side, by reformulating the equation \eqref{constraint16}, we have a new constraint $\forall i, \forall s$ as below,

@@

The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$.
The complexity order of this problem is about $O(\mathfrak{N} \times K)$.

@@

The complexity order of this algorithm is about $O(Slog(S)) + O(R\times \mathfrak{N})$.

@@

The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$.
As we mentioned before, the complexity order of the first sub-problem is about $O(N_u \times K)$
and the complexity order of the second sub-problem is about $O(Slog(S)) + O(R\times \mathfrak{N})$.
So the complexity of the main problem \eqref{problem} is $O(\mathfrak{N} \times K \times (Slog(S)+R\mathfrak{N}))$.

@@

The maximum number of VNF for each slice is 20 and the mean arrival rate for eMBB  is $\lambda  = 3Mbps$ and for mMTC and URLLC $\lambda  = 0.2Mbps$. 

@@

   Minimum data rate for URLLC and mMTC &  3 bits/sec/Hz \\ 

@@

Figure \ref{fig:8}, represents the aggregate throughput concerning the number of UEs and the maximum power for three different mMTC service instances. mMTC service includes a large number of UEs with low data rates and low power.
Assume each UE in each mMTC service instance requires $1bits/sec/Hz$ data rate and is not sensitive to end-to-end delay. The figure depicts that by increasing the number of UEs in each instance of the service, the aggregate throughput increases. Also, by increasing the maximum power of each UE in each instance of mMTC service, the aggregate throughput rises too.
\begin{figure}
  %\centering 
    \includegraphics[scale = 0.42]{mmTCpower.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput for mMTC services vs. Number of UE in each Service for three different mMTC service instances}
  \label{fig:8}
\end{figure}

Assume we have two types of eMBB service instances. In figure \ref{fig:9}, the aggregate throughput (by considering the priority factor $\delta_s$) is depicted for two eMBB service instances. Here we consider 4 UEs in each service. The figure \ref{fig:9} presented that by increasing the priority factor for one service instance, more resources are allocated to this service instance, and the aggregate throughput of this service is increased and vice versa. Also, we can realize from this figure that the aggregate throughput has the most significant value at the same priority.
\begin{figure}
  \centering 
    \includegraphics[scale = 0.4]{priorityLast.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput for two eMBB service instances vs. Priority of the first service instance }
  \label{fig:9}
\end{figure}
\section{Conclusion}\label{conc}
This paper proposed the downlink of the O-RAN system using network slicing for different types of 5G services (eMBB, mMTC, and URLC).
The isolation of various types of services (eMBB, mMTC, and URLC) in O-DU, O-CU, and user plane function (UPF) is accomplished.
Also, the paper aims to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the sum rate. The limited fronthaul capacity and the mean end-to-end delay for each service are considered. 
The problem is mixed-integer non-linear programming that is solved by the two-step iterative algorithm.
In the first step, we reformulated the problem to achieve the number of activated VNFs as a function of data rate. Then we obtain PRB association and power allocation using the Lagrangian method.
Then in the second step, O-RU association is acquired.
The performance of our proposed method (IAPPVO) is compared with the baseline scheme and FBDR in \cite{lee2018dynamic}. 
Also, we assume distinct scenarios for each service (eMBB, URLLC, and mMTC) based on their requirement QoS.
Simulation results depicts that the proposed method (IAPPVO) achieved $18.6\%$ higher data rate than the baseline scheme.
Moreover, simulation results illustrate less delay for the proposed method (IAPPVO) than FBDR and baseline scheme.

\bibliographystyle{IEEEtran} 
\bibliography{ref}
\end{document}
